An Elastica-driven Digital Curve Evolution Model for Image Segmentation\thanks{This work has been partially funded by CoMeDiC ANR-15-CE40-0006 research grant.}

### 2020-01-07 Revision/Biographies/biographies.tex
biographie daniel

\begin{document}
\paragraph{Daniel Antunes}
A brilliant PhD student from Brazil.

>>>>

\begin{document}
\paragraph{Daniel Antunes}
Daniel Antunes received his B.S. in computer science from the Universidade Federal do Rio de Janeiro, Brazil (2014) and his M.S. in  computer science from Université Paris-Est, France (2016). Since February 2017 he is a Ph.D student at the LAMA laboratory at Université Savoie Mont Blanc, France. His research interest is focused on digital geometry and combinatorial optimization applied to image analysis.
